---
title: "02-test project"
author: "Robert C Cline Sr"
date: '2022-04-07'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
```

## Undo Changes (Checkout, Revert and Reset)
Nathan's YouTube.  Click [here](https://www.youtube.com/watch?v=UmE0uf5UMzA&t=229)

This is a test document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.



```{r cars} 
library(kableExtra)
summary(cars) %>% 
kbl(caption = "Summary of the Cars dataset") %>% 
kable_classic(full_width = F, html_font = "Cambria", position = "left")  

```

### 1. `git revert`   Revert back to a prior commit.  

I am going to add some stuff here, then run a revert back to f341889  

This tutorial is great.  It illustrates the importance of making small commits.  I.e. one change at a time.  The issue, if you commit changes to several files, and you need to `git revert #hash`, you revert to the changes that are made to those files in *#hash*, and in subsequent files.   

In Nathan's words, you want your commits to be a `*chunk of something*` that you did.  

* Check out Nathan's video ~ 5:30 minutes.  

### 2. `git reset #hash` to reset your project back to a given commit.

* *git reset* is hard core because it  will remove commits.  

* `undo git reset`.  *git reset* will leave the unstaged changes in your working directory after reset.  These changes are temporary.  You *can* undo the reset if you do it immediately.  If you close the file, they are gone forever.  

  - git add . 
  - git commit -m "undo reset" 
  - this will add and commit the unstaged changes.
  - see Nathan's video @ 8:04/10:06  
 
### 3. `git reset #shaw --hard`  
 
 * This takes you back to the #shaw. All subsequent commits are gone forever.  
 
 
